---
title: "Regression Method/CI Analysis"
author: "Kayleigh Ryherd"
date: "10/26/2016"
output: html_document
---
# 15/70 Confidence Intervals 

## Table of Contents

1. [Linear Model with WASI Vocab](#linear-model-with-wasi-vocab)
    + [Group Differences](#group-differences-lm1)
2. [Linear Model with PPVT](#linear-model-with-ppvt)
    + [Group Differences](#group-differences-lm2)
3. [Linear Model with Vocabulary Composite](#linear-model-with-vocabulary-composite)
    + [Group Differences](#group-differences-lm3)
4. [Linear Model with Oral Comprehension](#linear-model-with-oral-comprehension)
    + [Group Differences](#group-differences-lm4)
5. [Robust Model with WASI Vocab](#robust-model-with-wasi-vocab)
    + [Group Differences](#group-differences-rlm1)
6. [Robust Model with PPVT](#robust-model-with-ppvt)
    + [Group Differences](#group-differences-rlm2)
7. [Robust Model with Vocabulary Composite](#robust-model-with-vocabulary-composite)
    + [Group Differences](#group-differences-rlm3)
8. [Robust Model with Oral Comprehension](#robust-model-with-oral-comprehension)
    + [Group Differences](#group-differences-rlm4)
9. [Group Sizes](#group-sizes)




Read in packages & data.
```{r, warning = FALSE, message = FALSE}
library(fBasics)
library(caret)
library(MASS)
library(ggplot2)
library(plyr)
library(reshape2)
library(xtable)
setwd("~/Dropbox/Definition_of_PCs/RegressionDefinitionMethod")
data <- read.csv("FullData_FinalMay23_2017.csv")
data <- data[data$handedness == "right",]
data$age.beh <- as.numeric(levels(data$age.beh))[data$age.beh]
```

Define some functions.

```{r}
# for plotting
gg_color_hue <- function(n) {
  hues = seq(15, 375, length=n+1)
  hcl(h=hues, l=65, c=100)[1:n]
}

# CIs to z-scores
ci2z <- function(ci)
{
  qnorm(ci + (1 - ci)/2)
}
```

Choose your CIs.

```{r}
ci.to.use <- c(.15, .70)
ci.title <- "CIs: 15%, 70%"
```

## Linear Model with WASI Vocab

Run model, get groups.
```{r}
model.data.lmwv <- data[, c(1, 3, 19, 8, 7, 21, 12)]
lmwv.cc <- model.data.lmwv[complete.cases(model.data.lmwv),]
## Checking predictors, outcome
dagoTest(lmwv.cc$decoding.comp)
dagoTest(lmwv.cc$wasi.matr.raw)
dagoTest(lmwv.cc$wasi.vocab.raw)
dagoTest(lmwv.cc$wj3.rcomp.raw)

## everything needs to be transformed except the decoding.comp, wasi vocab
vars_tf <- c("wasi.matr.raw", "wj3.rcomp.raw")
pp_md_tf <- preProcess(lmwv.cc[,vars_tf], method = c("center", "scale", "YeoJohnson"), na.remove=T)

#check the lambda values associated with the predictors
pp_md_tf$yj$wasi.matr.raw$lambda
pp_md_tf$yj$wj3.rcomp.raw$lambda

tf_data <- predict(pp_md_tf, lmwv.cc[,vars_tf])
lmwv.cc$wasi.matr.tf <- tf_data$wasi.matr.raw
lmwv.cc$wj3.rcomp.tf <- tf_data$wj3.rcomp.raw

dagoTest(lmwv.cc$wasi.matr.tf)
dagoTest(lmwv.cc$wj3.rcomp.tf)
# skewness has pretty much been fixed in all of them -- problem is just kurtosis

# center age
lmwv.cc$age.c <- lmwv.cc$age.beh - mean(lmwv.cc$age.beh, na.rm = TRUE)
# center/scale wasi vocab
lmwv.cc$wasi.vocab.cs <- scale(lmwv.cc$wasi.vocab.raw)
# composite has already been scaled

### Run regression
m1 <- lm(wj3.rcomp.tf ~ age.c + decoding.comp + wasi.matr.tf + wasi.vocab.cs, data = lmwv.cc)

#standardize predicted values
lmwv.cc$Pred <- predict(m1)
lmwv.cc$stdPred <- scale(lmwv.cc$Pred)

#obtained residuals
lmwv.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

lmwv.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
lmwv.cc$CI_group[lmwv.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.tf ~ stdPred, data=lmwv.cc)

p1 <- ggplot(lmwv.cc, aes(x=stdPred, y=wj3.rcomp.tf)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences LM1
Linear Model with WASI vocab

```{r}
# take away NSC group
lmwv.cc2 <- subset(lmwv.cc, CI_group != "NSC")
lmwv.cc2$CI_group <- as.factor(lmwv.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.tf ~ CI_group, data = lmwv.cc2)
summary(a1)
pairwise.t.test(lmwv.cc2$wj3.rcomp.tf, lmwv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmwv.cc2$wj3.rcomp.tf, list(lmwv.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = lmwv.cc2)
summary(a1)
pairwise.t.test(lmwv.cc2$age.c, lmwv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmwv.cc2$age.c, list(lmwv.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.tf ~ CI_group, data = lmwv.cc2)
summary(a1)
pairwise.t.test(lmwv.cc2$wasi.matr.tf, lmwv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmwv.cc2$wasi.matr.tf, list(lmwv.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decoding.comp ~ CI_group, data = lmwv.cc2)
summary(a1)
pairwise.t.test(lmwv.cc2$decoding.comp, lmwv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmwv.cc2$decoding.comp, list(lmwv.cc2$CI_group), mean)
```

### WASI Vocab
```{r}
a1 <- aov(wasi.vocab.cs ~ CI_group, data = lmwv.cc2)
summary(a1)
pairwise.t.test(lmwv.cc2$wasi.vocab.cs, lmwv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmwv.cc2$wasi.vocab.cs, list(lmwv.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
LM.WASI.Vocab <- data.frame(table(lmwv.cc$CI_group, lmwv.cc$handedness))
names(LM.WASI.Vocab) <- c("Group", "handedness", "lm.wasi.vocab")
LM.WASI.Vocab.r <- LM.WASI.Vocab[LM.WASI.Vocab$handedness == "right",]
LM.WASI.Vocab.r <- LM.WASI.Vocab.r[,-2]
```

## Linear Model with PPVT

Run model, get groups.
```{r}
model.data.lmpp <- data[, c(1, 3, 19, 8, 6, 21, 12)]
lmpp.cc <- model.data.lmpp[complete.cases(model.data.lmpp),]
## Checking predictors, outcome
dagoTest(lmpp.cc$decoding.comp)
dagoTest(lmpp.cc$wasi.matr.raw)
dagoTest(lmpp.cc$ppvt.raw)
dagoTest(lmpp.cc$wj3.rcomp.raw)

## everything needs to be transformed except the decoding.comp
vars_tf <- c("wasi.matr.raw", "ppvt.raw", "wj3.rcomp.raw")
pp_md_tf <- preProcess(lmpp.cc[,vars_tf], method = c("center", "scale", "YeoJohnson"), na.remove=T)

#check the lambda values associated with the predictors
pp_md_tf$yj$wasi.matr.raw$lambda
pp_md_tf$yj$ppvt.raw$lambda
pp_md_tf$yj$wj3.rcomp.raw$lambda

tf_data <- predict(pp_md_tf, lmpp.cc[,vars_tf])
lmpp.cc$wasi.matr.tf <- tf_data$wasi.matr.raw
lmpp.cc$ppvt.tf <- tf_data$ppvt.raw
lmpp.cc$wj3.rcomp.tf <- tf_data$wj3.rcomp.raw

dagoTest(lmpp.cc$wasi.matr.tf)
dagoTest(lmpp.cc$ppvt.tf)
dagoTest(lmpp.cc$wj3.rcomp.tf)
# skewness has pretty much been fixed in all of them -- problem is just kurtosis

# center age
lmpp.cc$age.c <- lmpp.cc$age.beh - mean(lmpp.cc$age.beh, na.rm = TRUE)
# composite has already been scaled

### Run regression
m1 <- lm(wj3.rcomp.tf ~ age.c + decoding.comp + wasi.matr.tf + ppvt.tf, data = lmpp.cc)

#standardize predicted values
lmpp.cc$Pred <- predict(m1)
lmpp.cc$stdPred <- scale(lmpp.cc$Pred)

#obtained residuals
lmpp.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

lmpp.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
lmpp.cc$CI_group[lmpp.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.tf ~ stdPred, data=lmpp.cc)

p1 <- ggplot(lmpp.cc, aes(x=stdPred, y=wj3.rcomp.tf)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences LM2
Linear Model with PPVT

```{r}
# take away NSC group
lmpp.cc2 <- subset(lmpp.cc, CI_group != "NSC")
lmpp.cc2$CI_group <- as.factor(lmpp.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.tf ~ CI_group, data = lmpp.cc2)
summary(a1)
pairwise.t.test(lmpp.cc2$wj3.rcomp.tf, lmpp.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmpp.cc2$wj3.rcomp.tf, list(lmpp.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = lmpp.cc2)
summary(a1)
pairwise.t.test(lmpp.cc2$age.c, lmpp.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmpp.cc2$age.c, list(lmpp.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.tf ~ CI_group, data = lmpp.cc2)
summary(a1)
pairwise.t.test(lmpp.cc2$wasi.matr.tf, lmpp.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmpp.cc2$wasi.matr.tf, list(lmpp.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decoding.comp ~ CI_group, data = lmpp.cc2)
summary(a1)
pairwise.t.test(lmpp.cc2$decoding.comp, lmpp.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmpp.cc2$decoding.comp, list(lmpp.cc2$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.tf ~ CI_group, data = lmpp.cc2)
summary(a1)
pairwise.t.test(lmpp.cc2$ppvt.tf, lmpp.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmpp.cc2$ppvt.tf, list(lmpp.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
LM.PPVT <- data.frame(table(lmpp.cc$CI_group, lmpp.cc$handedness))
names(LM.PPVT) <- c("Group", "handedness", "lm.ppvt")
LM.PPVT.r <- LM.PPVT[LM.PPVT$handedness == "right",]
LM.PPVT.r <- LM.PPVT.r[,-2]
```

## Linear Model with Vocabulary Composite

Run model, get groups.
```{r}
model.data.lmvc <- data[, c(1, 3, 19, 8, 22, 21, 12)]
lmvc.cc <- model.data.lmvc[complete.cases(model.data.lmvc),]
## Checking predictors, outcome
dagoTest(lmvc.cc$decoding.comp)
dagoTest(lmvc.cc$wasi.matr.raw)
dagoTest(lmvc.cc$vocab.comp)
dagoTest(lmvc.cc$wj3.rcomp.raw)

## everything needs to be transformed except the decoding.comp, vocab comp
vars_tf <- c("wasi.matr.raw", "wj3.rcomp.raw")
pp_md_tf <- preProcess(lmvc.cc[,vars_tf], method = c("center", "scale", "YeoJohnson"), na.remove=T)

#check the lambda values associated with the predictors
pp_md_tf$yj$wasi.matr.raw$lambda
pp_md_tf$yj$vocab.comp$lambda
pp_md_tf$yj$wj3.rcomp.raw$lambda

tf_data <- predict(pp_md_tf, lmvc.cc[,vars_tf])
lmvc.cc$wasi.matr.tf <- tf_data$wasi.matr.raw
lmvc.cc$wj3.rcomp.tf <- tf_data$wj3.rcomp.raw

dagoTest(lmvc.cc$wasi.matr.tf)
dagoTest(lmvc.cc$wj3.rcomp.tf)
# skewness has pretty much been fixed in all of them -- problem is just kurtosis

# center age
lmvc.cc$age.c <- lmvc.cc$age.beh - mean(lmvc.cc$age.beh, na.rm = TRUE)
# composites have already been scaled

### Run regression
m1 <- lm(wj3.rcomp.tf ~ age.c + decoding.comp + wasi.matr.tf + vocab.comp, data = lmvc.cc)

#standardize predicted values
lmvc.cc$Pred <- predict(m1)
lmvc.cc$stdPred <- scale(lmvc.cc$Pred)

#obtained residuals
lmvc.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

lmvc.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
lmvc.cc$CI_group[lmvc.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.tf ~ stdPred, data=lmvc.cc)

p1 <- ggplot(lmvc.cc, aes(x=stdPred, y=wj3.rcomp.tf)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences LM3
Linear Model with Vocab Composite

```{r}
# take away NSC group
lmvc.cc2 <- subset(lmvc.cc, CI_group != "NSC")
lmvc.cc2$CI_group <- as.factor(lmvc.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.tf ~ CI_group, data = lmvc.cc2)
summary(a1)
pairwise.t.test(lmvc.cc2$wj3.rcomp.tf, lmvc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmvc.cc2$wj3.rcomp.tf, list(lmvc.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = lmvc.cc2)
summary(a1)
pairwise.t.test(lmvc.cc2$age.c, lmvc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmvc.cc2$age.c, list(lmvc.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.tf ~ CI_group, data = lmvc.cc2)
summary(a1)
pairwise.t.test(lmvc.cc2$wasi.matr.tf, lmvc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmvc.cc2$wasi.matr.tf, list(lmvc.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decoding.comp ~ CI_group, data = lmvc.cc2)
summary(a1)
pairwise.t.test(lmvc.cc2$decoding.comp, lmvc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmvc.cc2$decoding.comp, list(lmvc.cc2$CI_group), mean)
```

### Vocab Composite
```{r}
a1 <- aov(vocab.comp ~ CI_group, data = lmvc.cc2)
summary(a1)
pairwise.t.test(lmvc.cc2$vocab.comp, lmvc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmvc.cc2$vocab.comp, list(lmvc.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
LM.VC <- data.frame(table(lmvc.cc$CI_group, lmvc.cc$handedness))
names(LM.VC) <- c("Group", "handedness", "lm.vocab.composite")
LM.VC.r <- LM.VC[LM.VC$handedness == "right",]
LM.VC.r <- LM.VC.r[,-2]
```

## Linear Model with Oral Comprehension

Run model, get groups.
```{r}
model.data.lmoc <- data[, c(1, 3, 19, 8, 13, 21, 12)]
lmoc.cc <- model.data.lmoc[complete.cases(model.data.lmoc),]
## Checking predictors, outcome
dagoTest(lmoc.cc$decoding.comp)
dagoTest(lmoc.cc$wasi.matr.raw)
dagoTest(lmoc.cc$wj3.oralcomp.raw)
dagoTest(lmoc.cc$wj3.rcomp.raw)

## everything needs to be transformed except the decoding.comp
vars_tf <- c("wasi.matr.raw", "wj3.oralcomp.raw", "wj3.rcomp.raw")
pp_md_tf <- preProcess(lmoc.cc[,vars_tf], method = c("center", "scale", "YeoJohnson"), na.remove=T)

#check the lambda values associated with the predictors
pp_md_tf$yj$wasi.matr.raw$lambda
pp_md_tf$yj$wj3.oralcomp$lambda
pp_md_tf$yj$wj3.rcomp.raw$lambda

tf_data <- predict(pp_md_tf, lmoc.cc[,vars_tf])
lmoc.cc$wasi.matr.tf <- tf_data$wasi.matr.raw
lmoc.cc$wj3.oralcomp.tf <- tf_data$wj3.oralcomp.raw
lmoc.cc$wj3.rcomp.tf <- tf_data$wj3.rcomp.raw

dagoTest(lmoc.cc$wasi.matr.tf)
dagoTest(lmoc.cc$wj3.oralcomp.tf)
dagoTest(lmoc.cc$wj3.rcomp.tf)
# skewness has pretty much been fixed in all of them -- problem is just kurtosis

# center age
lmoc.cc$age.c <- lmoc.cc$age.beh - mean(lmoc.cc$age.beh, na.rm = TRUE)
# composite has already been scaled

### Run regression
m1 <- lm(wj3.rcomp.tf ~ age.c + decoding.comp + wasi.matr.tf + wj3.oralcomp.tf, data = lmoc.cc)

#standardize predicted values
lmoc.cc$Pred <- predict(m1)
lmoc.cc$stdPred <- scale(lmoc.cc$Pred)

#obtained residuals
lmoc.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

lmoc.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
lmoc.cc$CI_group[lmoc.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.tf ~ stdPred, data=lmoc.cc)

p1 <- ggplot(lmoc.cc, aes(x=stdPred, y=wj3.rcomp.tf)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences LM4
Linear Model with Oral Comprehension

```{r}
# take away NSC group
lmoc.cc2 <- subset(lmoc.cc, CI_group != "NSC")
lmoc.cc2$CI_group <- as.factor(lmoc.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.tf ~ CI_group, data = lmoc.cc2)
summary(a1)
pairwise.t.test(lmoc.cc2$wj3.rcomp.tf, lmoc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmoc.cc2$wj3.rcomp.tf, list(lmoc.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = lmoc.cc2)
summary(a1)
pairwise.t.test(lmoc.cc2$age.c, lmoc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmoc.cc2$age.c, list(lmoc.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.tf ~ CI_group, data = lmoc.cc2)
summary(a1)
pairwise.t.test(lmoc.cc2$wasi.matr.tf, lmoc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmoc.cc2$wasi.matr.tf, list(lmoc.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decoding.comp ~ CI_group, data = lmoc.cc2)
summary(a1)
pairwise.t.test(lmoc.cc2$decoding.comp, lmoc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmoc.cc2$decoding.comp, list(lmoc.cc2$CI_group), mean)
```

### Oral Comprehension
```{r}
a1 <- aov(wj3.oralcomp.tf ~ CI_group, data = lmoc.cc2)
summary(a1)
pairwise.t.test(lmoc.cc2$wj3.oralcomp.tf, lmoc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(lmoc.cc2$wj3.oralcomp.tf, list(lmoc.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
LM.OC <- data.frame(table(lmoc.cc$CI_group, lmoc.cc$handedness))
names(LM.OC) <- c("Group", "handedness", "lm.oralcomp")
LM.OC.r <- LM.OC[LM.OC$handedness == "right",]
LM.OC.r <- LM.OC.r[,-2]
```

## Robust Model with WASI Vocab

Run model, get groups.
```{r}
model.data.rlmwv <- data[, c(1, 3, 19, 8, 7, 21, 12)]
rlmwv.cc <- model.data.rlmwv[complete.cases(model.data.rlmwv),]

# center and scale predictors
rlmwv.cc$wasi.matr.cs <- scale(rlmwv.cc$wasi.matr.raw)
rlmwv.cc$wasi.vocab.cs <- scale(rlmwv.cc$wasi.vocab.raw)
rlmwv.cc$wj3.rcomp.cs <- scale(rlmwv.cc$wj3.rcomp.raw)

# center age
rlmwv.cc$age.c <- rlmwv.cc$age.beh - mean(rlmwv.cc$age.beh, na.rm = TRUE)
# composite has already been scaled

### Run regression
m1 <- rlm(wj3.rcomp.cs ~ age.c + decoding.comp + wasi.matr.cs + wasi.vocab.cs, data = rlmwv.cc, method = "MM")

#standardize predicted values
rlmwv.cc$Pred <- predict(m1)
rlmwv.cc$stdPred <- scale(rlmwv.cc$Pred)

#obtained residuals
rlmwv.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

rlmwv.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
rlmwv.cc$CI_group[rlmwv.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.cs ~ stdPred, data=rlmwv.cc)

p1 <- ggplot(rlmwv.cc, aes(x=stdPred, y=wj3.rcomp.cs)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences RLM1
Robust Model with WASI Vocab

```{r}
# take away NSC group
rlmwv.cc2 <- subset(rlmwv.cc, CI_group != "NSC")
rlmwv.cc2$CI_group <- as.factor(rlmwv.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.cs ~ CI_group, data = rlmwv.cc2)
summary(a1)
pairwise.t.test(rlmwv.cc2$wj3.rcomp.cs, rlmwv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmwv.cc2$wj3.rcomp.cs, list(rlmwv.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = rlmwv.cc2)
summary(a1)
pairwise.t.test(rlmwv.cc2$age.c, rlmwv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmwv.cc2$age.c, list(rlmwv.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.cs ~ CI_group, data = rlmwv.cc2)
summary(a1)
pairwise.t.test(rlmwv.cc2$wasi.matr.cs, rlmwv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmwv.cc2$wasi.matr.cs, list(rlmwv.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decoding.comp ~ CI_group, data = rlmwv.cc2)
summary(a1)
pairwise.t.test(rlmwv.cc2$decoding.comp, rlmwv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmwv.cc2$decoding.comp, list(rlmwv.cc2$CI_group), mean)
```

### WASI Vocab
```{r}
a1 <- aov(wasi.vocab.cs ~ CI_group, data = rlmwv.cc2)
summary(a1)
pairwise.t.test(rlmwv.cc2$wasi.vocab.cs, rlmwv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmwv.cc2$wasi.vocab.cs, list(rlmwv.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
RLM.WV <- data.frame(table(rlmwv.cc$CI_group, rlmwv.cc$handedness))
names(RLM.WV) <- c("Group", "handedness", "rlm.wasi.vocab")
RLM.WV.r <- RLM.WV[RLM.WV$handedness == "right",]
RLM.WV.r <- RLM.WV.r[,-2]
```

## Robust Model with PPVT

Run model, get groups.
```{r}
model.data.rlmpp <- data[, c(1, 3, 19, 8, 6, 21, 12)]
rlmpp.cc <- model.data.rlmpp[complete.cases(model.data.rlmpp),]

# center and scale predictors
rlmpp.cc$wasi.matr.cs <- scale(rlmpp.cc$wasi.matr.raw)
rlmpp.cc$ppvt.cs <- scale(rlmpp.cc$ppvt.raw)
rlmpp.cc$wj3.rcomp.cs <- scale(rlmpp.cc$wj3.rcomp.raw)

# center age
rlmpp.cc$age.c <- rlmpp.cc$age.beh - mean(rlmpp.cc$age.beh, na.rm = TRUE)
# composite has already been scaled

### Run regression
m1 <- rlm(wj3.rcomp.cs ~ age.c + decoding.comp + wasi.matr.cs + ppvt.cs, data = rlmpp.cc, method = "MM")

#standardize predicted values
rlmpp.cc$Pred <- predict(m1)
rlmpp.cc$stdPred <- scale(rlmpp.cc$Pred)

#obtained residuals
rlmpp.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

rlmpp.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
rlmpp.cc$CI_group[rlmpp.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.cs ~ stdPred, data=rlmpp.cc)

p1 <- ggplot(rlmpp.cc, aes(x=stdPred, y=wj3.rcomp.cs)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences RLM2
Robust Model with PPVT

```{r}
# take away NSC group
rlmpp.cc2 <- subset(rlmpp.cc, CI_group != "NSC")
rlmpp.cc2$CI_group <- as.factor(rlmpp.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.cs ~ CI_group, data = rlmpp.cc2)
summary(a1)
pairwise.t.test(rlmpp.cc2$wj3.rcomp.cs, rlmpp.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmpp.cc2$wj3.rcomp.cs, list(rlmpp.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = rlmpp.cc2)
summary(a1)
pairwise.t.test(rlmpp.cc2$age.c, rlmpp.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmpp.cc2$age.c, list(rlmpp.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.cs ~ CI_group, data = rlmpp.cc2)
summary(a1)
pairwise.t.test(rlmpp.cc2$wasi.matr.cs, rlmpp.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmpp.cc2$wasi.matr.cs, list(rlmpp.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decoding.comp ~ CI_group, data = rlmpp.cc2)
summary(a1)
pairwise.t.test(rlmpp.cc2$decoding.comp, rlmpp.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmpp.cc2$decoding.comp, list(rlmpp.cc2$CI_group), mean)
```

### PPVT
```{r}
a1 <- aov(ppvt.cs ~ CI_group, data = rlmpp.cc2)
summary(a1)
pairwise.t.test(rlmpp.cc2$ppvt.cs, rlmpp.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmpp.cc2$ppvt.cs, list(rlmpp.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
RLM.PP <- data.frame(table(rlmpp.cc$CI_group, rlmpp.cc$handedness))
names(RLM.PP) <- c("Group", "handedness", "rlm.ppvt")
RLM.PP.r <- RLM.PP[RLM.PP$handedness == "right",]
RLM.PP.r <- RLM.PP.r[,-2]
```

## Robust Model with Vocab Composite

Run model, get groups.
```{r}
model.data.rlmvc <- data[, c(1, 3, 19, 8, 22, 21, 12)]
rlmvc.cc <- model.data.rlmvc[complete.cases(model.data.rlmvc),]

# center and scale predictors
rlmvc.cc$wasi.matr.cs <- scale(rlmvc.cc$wasi.matr.raw)
rlmvc.cc$wj3.rcomp.cs <- scale(rlmvc.cc$wj3.rcomp.raw)

# center age
rlmvc.cc$age.c <- rlmvc.cc$age.beh - mean(rlmvc.cc$age.beh, na.rm = TRUE)
# composites have already been scaled

### Run regression
m1 <- rlm(wj3.rcomp.cs ~ age.c + decoding.comp + wasi.matr.cs + vocab.comp, data = rlmvc.cc, method = "MM")

#standardize predicted values
rlmvc.cc$Pred <- predict(m1)
rlmvc.cc$stdPred <- scale(rlmvc.cc$Pred)

#obtained residuals
rlmvc.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

rlmvc.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
rlmvc.cc$CI_group[rlmvc.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.cs ~ stdPred, data=rlmvc.cc)

p1 <- ggplot(rlmvc.cc, aes(x=stdPred, y=wj3.rcomp.cs)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences RLM3
Robust Model with Vocab Composite

```{r}
# take away NSC group
rlmvc.cc2 <- subset(rlmvc.cc, CI_group != "NSC")
rlmvc.cc2$CI_group <- as.factor(rlmvc.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.cs ~ CI_group, data = rlmvc.cc2)
summary(a1)
pairwise.t.test(rlmvc.cc2$wj3.rcomp.cs, rlmvc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmvc.cc2$wj3.rcomp.cs, list(rlmvc.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = rlmvc.cc2)
summary(a1)
pairwise.t.test(rlmvc.cc2$age.c, rlmvc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmvc.cc2$age.c, list(rlmvc.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.cs ~ CI_group, data = rlmvc.cc2)
summary(a1)
pairwise.t.test(rlmvc.cc2$wasi.matr.cs, rlmvc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmvc.cc2$wasi.matr.cs, list(rlmvc.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decoding.comp ~ CI_group, data = rlmvc.cc2)
summary(a1)
pairwise.t.test(rlmvc.cc2$decoding.comp, rlmvc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmvc.cc2$decoding.comp, list(rlmvc.cc2$CI_group), mean)
```

### Vocab Composite
```{r}
a1 <- aov(vocab.comp ~ CI_group, data = rlmvc.cc2)
summary(a1)
pairwise.t.test(rlmvc.cc2$vocab.comp, rlmvc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmvc.cc2$vocab.comp, list(rlmvc.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
RLM.VC <- data.frame(table(rlmvc.cc$CI_group, rlmvc.cc$handedness))
names(RLM.VC) <- c("Group", "handedness", "rlm.ppvt")
RLM.VC.r <- RLM.VC[RLM.VC$handedness == "right",]
RLM.VC.r <- RLM.VC.r[,-2]
```

## Robust Model with Oral Comprehension

Run model, get groups.
```{r}
model.data.rlmoc <- data[, c(1, 3, 19, 8, 13, 21, 12)]
rlmoc.cc <- model.data.rlmoc[complete.cases(model.data.rlmoc),]

# center and scale predictors
rlmoc.cc$wasi.matr.cs <- scale(rlmoc.cc$wasi.matr.raw)
rlmoc.cc$wj3.rcomp.cs <- scale(rlmoc.cc$wj3.rcomp.raw)
rlmoc.cc$wj3.oralcomp.cs <- scale(rlmoc.cc$wj3.oralcomp.raw)

# center age
rlmoc.cc$age.c <- rlmoc.cc$age.beh - mean(rlmoc.cc$age.beh, na.rm = TRUE)
# composites have already been scaled

### Run regression
m1 <- rlm(wj3.rcomp.cs ~ age.c + decoding.comp + wasi.matr.cs + wj3.oralcomp.cs, data = rlmoc.cc, method = "MM")

#standardize predicted values
rlmoc.cc$Pred <- predict(m1)
rlmoc.cc$stdPred <- scale(rlmoc.cc$Pred)

#obtained residuals
rlmoc.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

rlmoc.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
rlmoc.cc$CI_group[rlmoc.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.cs ~ stdPred, data=rlmoc.cc)

p1 <- ggplot(rlmoc.cc, aes(x=stdPred, y=wj3.rcomp.cs)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences RLM4
Robust Model with Oral Comprehension
```{r}
# take away NSC group
rlmoc.cc2 <- subset(rlmoc.cc, CI_group != "NSC")
rlmoc.cc2$CI_group <- as.factor(rlmoc.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.cs ~ CI_group, data = rlmoc.cc2)
summary(a1)
pairwise.t.test(rlmoc.cc2$wj3.rcomp.cs, rlmoc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmoc.cc2$wj3.rcomp.cs, list(rlmoc.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = rlmoc.cc2)
summary(a1)
pairwise.t.test(rlmoc.cc2$age.c, rlmoc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmoc.cc2$age.c, list(rlmoc.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.cs ~ CI_group, data = rlmoc.cc2)
summary(a1)
pairwise.t.test(rlmoc.cc2$wasi.matr.cs, rlmoc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmoc.cc2$wasi.matr.cs, list(rlmoc.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decoding.comp ~ CI_group, data = rlmoc.cc2)
summary(a1)
pairwise.t.test(rlmoc.cc2$decoding.comp, rlmoc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmoc.cc2$decoding.comp, list(rlmoc.cc2$CI_group), mean)
```

### Oral Comprehension
```{r}
a1 <- aov(wj3.oralcomp.cs ~ CI_group, data = rlmoc.cc2)
summary(a1)
pairwise.t.test(rlmoc.cc2$wj3.oralcomp.cs, rlmoc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(rlmoc.cc2$wj3.oralcomp.cs, list(rlmoc.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
RLM.OC <- data.frame(table(rlmoc.cc$CI_group, rlmoc.cc$handedness))
names(RLM.OC) <- c("Group", "handedness", "rlm.ppvt")
RLM.OC.r <- RLM.OC[RLM.OC$handedness == "right",]
RLM.OC.r <- RLM.OC.r[,-2]
```

## Group Sizes
 Across analyses
 
```{r, results = "asis"}
group.sizes <- cbind(LM.WASI.Vocab.r, LM.PPVT.r[,2], LM.VC.r[,2], LM.OC.r[,2], RLM.WV.r[,2], RLM.PP.r[,2], RLM.VC.r[,2], RLM.OC.r[,2])
names(group.sizes) <- c("group", "LM1 (WASI Vocab)", "LM2 (PPVT)", "LM3 (Vocab Composite)", "LM4 (Oral Comp)", "RLM1 (WASI Vocab)", "RLM2 (PPVT)", "RLM3 (Vocab Composite)", "RLM4 (Oral Comp)")
gs <- xtable(group.sizes)
print(gs, type ="html", include.rownames = FALSE)
```



