---
title: "Regression Method/CI Analysis"
author: "Kayleigh Ryherd"
date: "10/26/2016"
output: html_document
---
# 20/60 Confidence Intervals 

## Table of Contents

1. [Robust Model Without Vocab](#robust-model-without-vocabulary)
    + [Group Differences](#group-differences-1)
2. [Robust Model With Vocab (WASI)](#robust-model-with-vocabulary)
    + [Group Differences](#group-differences-2)
3. [Robust Model With Oral Comprehension](#robust-model-with-oral-comprehension)
    + [Group Differences](#group-differences-3)
4. [Robust Model With Vocab (PPVT)](#robust-model-with-ppvt)
    + [Group Differences](#group-differences-4)
5. [Linear Model With Vocab (PPVT)](#linear-model-with-ppvt)
    + [Group Differences](#group-differences-5)
6. [Group Sizes](#group-sizes)




Read in packages & data.
```{r, warning = FALSE, message = FALSE}
library(fBasics)
library(caret)
library(MASS)
library(ggplot2)
library(plyr)
library(reshape2)
setwd("~/Dropbox/Definition_of_PCs/Sept2016")
data <- read.csv("FullExport_NoOverlap_11-1-16.csv")
comp <- read.csv("decoding_composite.csv")
comp <- comp[,-1]
data <- merge(data, comp, by = "SubjectID")
```

Define some functions.

```{r}
# for plotting
gg_color_hue <- function(n) {
  hues = seq(15, 375, length=n+1)
  hcl(h=hues, l=65, c=100)[1:n]
}

# CIs to z-scores
ci2z <- function(ci)
{
  qnorm(ci + (1 - ci)/2)
}
```

Choose your CIs.

```{r}
ci.to.use <- c(.20, .60)
ci.title <- "CIs: 20%, 60%"
```

## Robust Model without Vocabulary

Run model, get groups.
```{r}
model.data.nv <- data[, c(1, 2, 7, 11, 18, 19)]
nv.cc <- model.data.nv[complete.cases(model.data.nv),]
#just centering
nv.cc$age.c <- nv.cc$age - mean(nv.cc$age, na.rm = TRUE)
#centering and scaling
nv.cc$wj3.rcomp.cs <- scale(nv.cc$wj3.rcomp.raw)
nv.cc$wasi.matr.cs <- scale(nv.cc$wasi.matr.raw)

### Run regression
m1 <- rlm(wj3.rcomp.cs ~ age.c + composite1 + wasi.matr.cs, data = nv.cc, method = "MM")

#standardize predicted values
nv.cc$Pred <- predict(m1)
nv.cc$stdPred <- scale(nv.cc$Pred)

#obtained residuals
nv.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

nv.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
nv.cc$CI_group[nv.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.cs ~ stdPred, data=nv.cc)

p1 <- ggplot(nv.cc, aes(x=stdPred, y=wj3.rcomp.cs)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences 1
Robust Model without Vocabulary

```{r}
# take away NSC group
nv.cc2 <- subset(nv.cc, CI_group != "NSC")
nv.cc2$CI_group <- as.factor(nv.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.cs ~ CI_group, data = nv.cc2)
summary(a1)
pairwise.t.test(nv.cc2$wj3.rcomp.cs, nv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(nv.cc2$wj3.rcomp.cs, list(nv.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = nv.cc2)
summary(a1)
pairwise.t.test(nv.cc2$age.c, nv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(nv.cc2$age.c, list(nv.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.cs ~ CI_group, data = nv.cc2)
summary(a1)
pairwise.t.test(nv.cc2$wasi.matr.cs, nv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(nv.cc2$wasi.matr.cs, list(nv.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(composite1 ~ CI_group, data = nv.cc2)
summary(a1)
pairwise.t.test(nv.cc2$composite1, nv.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(nv.cc2$composite1, list(nv.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
Robust.Without.Vocab <- data.frame(table(nv.cc$CI_group, nv.cc$handedness))
names(Robust.Without.Vocab) <- c("Group", "handedness", "rlm.w/o.vocab")
Robust.Without.Vocab.r <- Robust.Without.Vocab[Robust.Without.Vocab$handedness == "right",]
Robust.Without.Vocab.r <- Robust.Without.Vocab.r[,-2]
```

## Robust Model with Vocabulary

Run model, get groups.
```{r}
model.data.v <- data[, c(1, 2, 6, 7, 11, 18, 19)]
v.cc <- model.data.v[complete.cases(model.data.v),]
#just centering
v.cc$age.c <- v.cc$age - mean(v.cc$age, na.rm = TRUE)
#centering and scaling
v.cc$wj3.rcomp.cs <- scale(v.cc$wj3.rcomp.raw)
v.cc$wasi.matr.cs <- scale(v.cc$wasi.matr.raw)
v.cc$wasi.vocab.cs <- scale(v.cc$wasi.vocab.raw)

### Run regression
m1 <- rlm(wj3.rcomp.cs ~ age.c + composite1 + wasi.matr.cs + wasi.vocab.cs, data = v.cc, method = "MM")

#standardize predicted values
v.cc$Pred <- predict(m1)
v.cc$stdPred <- scale(v.cc$Pred)

#obtained residuals
v.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

v.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
v.cc$CI_group[v.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.cs ~ stdPred, data=v.cc)

p1 <- ggplot(v.cc, aes(x=stdPred, y=wj3.rcomp.cs)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences 2
Robust Model with Vocabulary

```{r}
# take away NSC group
v.cc2 <- subset(v.cc, CI_group != "NSC")
v.cc2$CI_group <- as.factor(v.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.cs ~ CI_group, data = v.cc2)
summary(a1)
pairwise.t.test(v.cc2$wj3.rcomp.cs, v.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(v.cc2$wj3.rcomp.cs, list(v.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = v.cc2)
summary(a1)
pairwise.t.test(v.cc2$age.c, v.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(v.cc2$age.c, list(v.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.cs ~ CI_group, data = v.cc2)
summary(a1)
pairwise.t.test(v.cc2$wasi.matr.cs, v.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(v.cc2$wasi.matr.cs, list(v.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(composite1 ~ CI_group, data = v.cc2)
summary(a1)
pairwise.t.test(v.cc2$composite1, v.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(v.cc2$composite1, list(v.cc2$CI_group), mean)
```

### Vocab
```{r}
a1 <- aov(wasi.vocab.cs ~ CI_group, data = v.cc2)
summary(a1)
pairwise.t.test(v.cc2$wasi.vocab.cs, v.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(v.cc2$wasi.vocab.cs, list(v.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
Robust.With.Vocab <- data.frame(table(v.cc$CI_group, v.cc$handedness))
names(Robust.With.Vocab) <- c("Group", "handedness", "rlm.w.vocab")
Robust.With.Vocab.r <- Robust.With.Vocab[Robust.With.Vocab$handedness == "right",]
Robust.With.Vocab.r <- Robust.With.Vocab.r[,-2]
```

## Robust Model with Oral Comprehension

Run model, get groups.
```{r}
model.data.oc <- data[, c(1, 2, 6, 7, 11, 12, 18, 19)]
oc.cc <- model.data.oc[complete.cases(model.data.oc),]
#just centering
oc.cc$age.c <- oc.cc$age - mean(oc.cc$age, na.rm = TRUE)
#centering and scaling
oc.cc$wj3.rcomp.cs <- scale(oc.cc$wj3.rcomp.raw)
oc.cc$wasi.matr.cs <- scale(oc.cc$wasi.matr.raw)
oc.cc$wasi.vocab.cs <- scale(oc.cc$wasi.vocab.raw)
oc.cc$wj3.oralcomp.cs <- scale(oc.cc$wj3.oralcomp.raw)

### Run regression
m1 <- rlm(wj3.rcomp.cs ~ age.c + composite1 + wasi.matr.cs + wj3.oralcomp.cs, data = oc.cc, method = "MM")

#standardize predicted values
oc.cc$Pred <- predict(m1)
oc.cc$stdPred <- scale(oc.cc$Pred)

#obtained residuals
oc.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

oc.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
oc.cc$CI_group[oc.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.cs ~ stdPred, data=oc.cc)

p1 <- ggplot(oc.cc, aes(x=stdPred, y=wj3.rcomp.cs)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences 3
Robust Model with Oral Comprehension

```{r}
# take away NSC group
oc.cc2 <- subset(oc.cc, CI_group != "NSC")
oc.cc2$CI_group <- as.factor(oc.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.cs ~ CI_group, data = oc.cc2)
summary(a1)
pairwise.t.test(oc.cc2$wj3.rcomp.cs, oc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(oc.cc2$wj3.rcomp.cs, list(oc.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = oc.cc2)
summary(a1)
pairwise.t.test(oc.cc2$age.c, oc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(oc.cc2$age.c, list(oc.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.cs ~ CI_group, data = oc.cc2)
summary(a1)
pairwise.t.test(oc.cc2$wasi.matr.cs, oc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(oc.cc2$wasi.matr.cs, list(oc.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(composite1 ~ CI_group, data = oc.cc2)
summary(a1)
pairwise.t.test(oc.cc2$composite1, oc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(oc.cc2$composite1, list(oc.cc2$CI_group), mean)
```

### Oral Comprehension
```{r}
a1 <- aov(wj3.oralcomp.cs ~ CI_group, data = oc.cc2)
summary(a1)
pairwise.t.test(oc.cc2$wj3.oralcomp.cs, oc.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(oc.cc2$wj3.oralcomp.cs, list(oc.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
Robust.With.OralComp <- data.frame(table(oc.cc$CI_group, oc.cc$handedness))
names(Robust.With.OralComp) <- c("Group", "handedness", "rlm.w.oralcomp")
Robust.With.OralComp.r <- Robust.With.OralComp[Robust.With.OralComp$handedness == "right",]
Robust.With.OralComp.r <- Robust.With.OralComp.r[,-2]
```

## Robust Model with PPVT

Run model, get groups.
```{r}
model.data.pm <- data[, c(1, 2, 5, 7, 11, 12, 18, 19)]
pm.cc <- model.data.pm[complete.cases(model.data.pm),]
#just centering
pm.cc$age.c <- pm.cc$age - mean(pm.cc$age, na.rm = TRUE)
#centering and scaling
pm.cc$wj3.rcomp.cs <- scale(pm.cc$wj3.rcomp.raw)
pm.cc$wasi.matr.cs <- scale(pm.cc$wasi.matr.raw)
pm.cc$ppvt.cs <- scale(pm.cc$ppvt.raw)
pm.cc$wj3.oralcomp.cs <- scale(pm.cc$wj3.oralcomp.raw)

### Run regression
m1 <- rlm(wj3.rcomp.cs ~ age.c + composite1 + wasi.matr.cs + ppvt.cs, data = pm.cc, method = "MM")

#standardize predicted values
pm.cc$Pred <- predict(m1)
pm.cc$stdPred <- scale(pm.cc$Pred)

#obtained residuals
pm.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

pm.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
pm.cc$CI_group[pm.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.cs ~ stdPred, data=pm.cc)

p1 <- ggplot(pm.cc, aes(x=stdPred, y=wj3.rcomp.cs)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences 4
Robust Model with PPVT

```{r}
# take away NSC group
pm.cc2 <- subset(pm.cc, CI_group != "NSC")
pm.cc2$CI_group <- as.factor(pm.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.cs ~ CI_group, data = pm.cc2)
summary(a1)
pairwise.t.test(pm.cc2$wj3.rcomp.cs, pm.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(pm.cc2$wj3.rcomp.cs, list(pm.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = pm.cc2)
summary(a1)
pairwise.t.test(pm.cc2$age.c, pm.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(pm.cc2$age.c, list(pm.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.cs ~ CI_group, data = pm.cc2)
summary(a1)
pairwise.t.test(pm.cc2$wasi.matr.cs, pm.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(pm.cc2$wasi.matr.cs, list(pm.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(composite1 ~ CI_group, data = pm.cc2)
summary(a1)
pairwise.t.test(pm.cc2$composite1, pm.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(pm.cc2$composite1, list(pm.cc2$CI_group), mean)
```

### Oral Comprehension
```{r}
a1 <- aov(wj3.oralcomp.cs ~ CI_group, data = pm.cc2)
summary(a1)
pairwise.t.test(pm.cc2$wj3.oralcomp.cs, pm.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(pm.cc2$wj3.oralcomp.cs, list(pm.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
Robust.With.PPVT <- data.frame(table(pm.cc$CI_group, pm.cc$handedness))
names(Robust.With.PPVT) <- c("Group", "handedness", "rlm.w.ppvt")
Robust.With.PPVT.r <- Robust.With.PPVT[Robust.With.PPVT$handedness == "right",]
Robust.With.PPVT.r <- Robust.With.PPVT.r[,-2]
```

## Linear Model with PPVT

Run model, get groups.
```{r}
model.data.plm <- data[, c(1, 2, 5, 7, 11, 12, 18, 19)]
plm.cc <- model.data.plm[complete.cases(model.data.plm),]
## Checking predictors, outcome
dagoTest(plm.cc$composite1)
dagoTest(plm.cc$wasi.matr.raw)
dagoTest(plm.cc$ppvt.raw)
dagoTest(plm.cc$wj3.rcomp.raw)

## everything needs to be transformed except the composite
vars_tf <- c("wasi.matr.raw","ppvt.raw","wj3.rcomp.raw")
pp_md_tf <- preProcess(data[,vars_tf], method = c("center", "scale", "YeoJohnson"), na.remove=T)

#check the lambda values associated with the predictors
pp_md_tf$yj$wasi.matr.raw$lambda
pp_md_tf$yj$ppvt.raw$lambda
pp_md_tf$yj$wj3.rcomp.raw$lambda
## ppvt lambda is still high
x <- density(plm.cc$ppvt.raw, bw="SJ", na.rm=T)
plot(x)
# no obvious outlier?
tf_data <- predict(pp_md_tf, plm.cc[,vars_tf])
plm.cc$wasi.matr.tf <- tf_data$wasi.matr.raw
plm.cc$ppvt.tf <- tf_data$ppvt.raw
plm.cc$wj3.rcomp.tf <- tf_data$wj3.rcomp.raw

dagoTest(plm.cc$wasi.matr.tf)
dagoTest(plm.cc$ppvt.tf)
dagoTest(plm.cc$wj3.rcomp.tf)
# skewness has pretty much been fixed in all of them -- problem is just kurtosis

plm.cc$age.c <- plm.cc$age - mean(plm.cc$age, na.rm = TRUE)

### Run regression
m1 <- lm(wj3.rcomp.tf~ age.c + composite1 + wasi.matr.tf + ppvt.tf, data = plm.cc)

#standardize predicted values
plm.cc$Pred <- predict(m1)
plm.cc$stdPred <- scale(plm.cc$Pred)

#obtained residuals
plm.cc$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

plm.cc$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
plm.cc$CI_group[plm.cc$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.tf ~ stdPred, data=plm.cc)

p1 <- ggplot(plm.cc, aes(x=stdPred, y=wj3.rcomp.tf)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("WJ3 Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences 5
Linear Model with PPVT

```{r}
# take away NSC group
plm.cc2 <- subset(plm.cc, CI_group != "NSC")
plm.cc2$CI_group <- as.factor(plm.cc2$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.tf ~ CI_group, data = plm.cc2)
summary(a1)
pairwise.t.test(plm.cc2$wj3.rcomp.tf, plm.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(plm.cc2$wj3.rcomp.tf, list(plm.cc2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.c ~ CI_group, data = plm.cc2)
summary(a1)
pairwise.t.test(plm.cc2$age.c, plm.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(plm.cc2$age.c, list(plm.cc2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.tf ~ CI_group, data = plm.cc2)
summary(a1)
pairwise.t.test(plm.cc2$wasi.matr.tf, plm.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(plm.cc2$wasi.matr.tf, list(plm.cc2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(composite1 ~ CI_group, data = plm.cc2)
summary(a1)
pairwise.t.test(plm.cc2$composite1, plm.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(plm.cc2$composite1, list(plm.cc2$CI_group), mean)
```

### Vocab
```{r}
a1 <- aov(ppvt.tf ~ CI_group, data = plm.cc2)
summary(a1)
pairwise.t.test(plm.cc2$ppvt.tf, plm.cc2$CI_group, p.adjust.method = "bonferroni")
aggregate(plm.cc2$ppvt.tf, list(plm.cc2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
LM.With.PPVT <- data.frame(table(plm.cc$CI_group, plm.cc$handedness))
names(LM.With.PPVT) <- c("Group", "handedness", "lm.w.ppvt")
LM.With.PPVT.r <- LM.With.PPVT[LM.With.PPVT$handedness == "right",]
LM.With.PPVT.r <- LM.With.PPVT.r[,-2]
```

## Group Sizes
 
Across analyses
```{r}
group.sizes <- cbind(Robust.With.Vocab.r, Robust.Without.Vocab.r[,2], Robust.With.OralComp.r[,2], Robust.With.PPVT.r[,2], LM.With.PPVT.r[,2])
names(group.sizes) <- c("group", "rlm.w.vocab", "rlm.wo.vocab", "rlm.w.oralcomp", "rlm.w.ppvt", "lm.w.ppvt")
print(group.sizes)
```