---
title: "UPC Analysis"
author: "Kayleigh Ryherd"
date: "9/13/2017"
output: html_document
---

# 15/70 Confidence Intervals 

Read in packages & data.
```{r, warning = FALSE, message = FALSE}
library(fBasics)
library(caret)
library(MASS)
library(ggplot2)
library(plyr)
library(reshape2)
library(xtable)
setwd("~/Dropbox/Definition_of_PCs/RegressionDefinitionMethod/MultipleCompTests-Aug2017/RegressionMethod/CheckingInfluentialPoints_Nov292017")
data2 <- read.csv("AllDataImputed_Nov292017.csv")
```

Remove influential subjects (#62 and #97)

```{r}
# finding the indices for these subjects
which(data2$SubjectID == 62)
which(data2$SubjectID == 97)

#removing these subjects
data2 <- data2[-c(568, 599),]
```

Define some functions.

```{r}
# for plotting
gg_color_hue <- function(n) {
  hues = seq(15, 375, length=n+1)
  hcl(h=hues, l=65, c=100)[1:n]
}

# CIs to z-scores
ci2z <- function(ci)
{
  qnorm(ci + (1 - ci)/2)
}
```

```{r}
ci.to.use <- c(.15, .70)
ci.title <- "CIs: 15%, 70%"
ci.doc <- "15_70"
```

## KTEA

# No interaction

Run model, get groups.
```{r}

m1 <- lm(ktea2.t ~ age.tested.c + decode + wasi.matr.t + ppvt.t, data = data2)

#standardize predicted values
data2$Pred <- predict(m1)
data2$stdPred <- scale(data2$Pred)

#obtained residuals
data2$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

data2$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
data2$CI_group[data2$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(ktea2.t ~ stdPred, data=data2)

p1 <- ggplot(data2, aes(x=stdPred, y=ktea2.t)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences KTEA

```{r}
# take away NSC group
data3 <- subset(data2, CI_group != "NSC")
data3$CI_group <- as.factor(data3$CI_group)
write.csv(data3, paste("KTEANoInt-",ci.doc,".csv", sep=""))
```

### Reading Comprehension
```{r}
a1 <- aov(ktea2.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$ktea2.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$ktea2.t, list(data3$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$age.tested.c, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$age.tested.c, list(data3$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$wasi.matr.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$wasi.matr.t, list(data3$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$decode, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$decode, list(data3$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$ppvt.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$ppvt.t, list(data3$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
KTEA.res <- data.frame(table(data2$CI_group))
names(KTEA.res) <- c("Group","KTEA")
```

# Interaction

Run model, get groups.
```{r}

m1 <- lm(ktea2.t ~ age.tested.c * decode * wasi.matr.t * ppvt.t, data = data2)

#standardize predicted values
data2$Pred <- predict(m1)
data2$stdPred <- scale(data2$Pred)

#obtained residuals
data2$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

data2$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
data2$CI_group[data2$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(ktea2.t ~ stdPred, data=data2)

p1 <- ggplot(data2, aes(x=stdPred, y=ktea2.t)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences KTEA Interaction

```{r}
# take away NSC group
data3 <- subset(data2, CI_group != "NSC")
data3$CI_group <- as.factor(data3$CI_group)
write.csv(data3, paste("KTEAInt-",ci.doc,".csv", sep=""))
```

### Reading Comprehension
```{r}
a1 <- aov(ktea2.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$ktea2.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$ktea2.t, list(data3$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$age.tested.c, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$age.tested.c, list(data3$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$wasi.matr.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$wasi.matr.t, list(data3$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$decode, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$decode, list(data3$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$ppvt.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$ppvt.t, list(data3$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
KTEA.resi <- data.frame(table(data2$CI_group))
names(KTEA.resi) <- c("Group","KTEAi")
```

## WJ

# No interaction

Run model, get groups.
```{r}

m1 <- lm(wj3.rcomp.t ~ age.tested.c + decode + wasi.matr.t + ppvt.t, data = data2)

#standardize predicted values
data2$Pred <- predict(m1)
data2$stdPred <- scale(data2$Pred)

#obtained residuals
data2$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

data2$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
data2$CI_group[data2$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.t ~ stdPred, data=data2)

p1 <- ggplot(data2, aes(x=stdPred, y=wj3.rcomp.t)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences WJ3

```{r}
# take away NSC group
data3 <- subset(data2, CI_group != "NSC")
data3$CI_group <- as.factor(data3$CI_group)
write.csv(data3, paste("WJ3NoInt-",ci.doc,".csv", sep=""))
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$wj3.rcomp.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$wj3.rcomp.t, list(data3$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$age.tested.c, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$age.tested.c, list(data3$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$wasi.matr.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$wasi.matr.t, list(data3$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$decode, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$decode, list(data3$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$ppvt.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$ppvt.t, list(data3$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
WJ3.res <- data.frame(table(data2$CI_group))
names(WJ3.res) <- c("Group","WJ3")
```

# Interaction

Run model, get groups.
```{r}

m1 <- lm(wj3.rcomp.t ~ age.tested.c * decode * wasi.matr.t * ppvt.t, data = data2)

#standardize predicted values
data2$Pred <- predict(m1)
data2$stdPred <- scale(data2$Pred)

#obtained residuals
data2$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

data2$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
data2$CI_group[data2$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.t ~ stdPred, data=data2)

p1 <- ggplot(data2, aes(x=stdPred, y=wj3.rcomp.t)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences WJ3 Interaction

```{r}
# take away NSC group
data3 <- subset(data2, CI_group != "NSC")
data3$CI_group <- as.factor(data3$CI_group)
write.csv(data3, paste("WJ3Int-",ci.doc,".csv", sep=""))
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$wj3.rcomp.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$wj3.rcomp.t, list(data3$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$age.tested.c, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$age.tested.c, list(data3$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$wasi.matr.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$wasi.matr.t, list(data3$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$decode, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$decode, list(data3$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$ppvt.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$ppvt.t, list(data3$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
WJ3.resi <- data.frame(table(data2$CI_group))
names(WJ3.resi) <- c("Group","WJ3i")
```

## RC Composite

```{r}

m1 <- lm(rc.comp ~ age.tested.c + decode + wasi.matr.t + ppvt.t, data = data2)

#standardize predicted values
data2$Pred <- predict(m1)
data2$stdPred <- scale(data2$Pred)

#obtained residuals
data2$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

data2$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
data2$CI_group[data2$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(rc.comp ~ stdPred, data=data2)

p1 <- ggplot(data2, aes(x=stdPred, y=rc.comp)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences Composite No Interaction

```{r}
# take away NSC group
data3 <- subset(data2, CI_group != "NSC")
data3$CI_group <- as.factor(data3$CI_group)
write.csv(data3, paste("CompositeNoInt-",ci.doc,".csv", sep=""))
```

### Reading Comprehension
```{r}
a1 <- aov(rc.comp ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$rc.comp, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$rc.comp, list(data3$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$age.tested.c, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$age.tested.c, list(data3$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$wasi.matr.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$wasi.matr.t, list(data3$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$decode, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$decode, list(data3$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$ppvt.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$ppvt.t, list(data3$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
RC.res <- data.frame(table(data2$CI_group))
names(RC.res) <- c("Group","RC")
```

## Interaction

```{r}
data2i <- data2

m1 <- lm(rc.comp ~ age.tested.c * decode * wasi.matr.t * ppvt.t, data = data2i)

#standardize predicted values
data2i$Pred <- predict(m1)
data2i$stdPred <- scale(data2i$Pred)

#obtained residuals
data2i$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

data2i$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
data2i$CI_group[data2i$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(rc.comp ~ stdPred, data=data2i)

p1 <- ggplot(data2i, aes(x=stdPred, y=rc.comp)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Reading Comprehension") +
  ggtitle(ci.title)
```


## Group Differences Composite Interaction

```{r}
# take away NSC group
data3 <- subset(data2i, CI_group != "NSC")
data3$CI_group <- as.factor(data3$CI_group)
write.csv(data3, paste("CompositeInt-",ci.doc,".csv", sep=""))
```

### Reading Comprehension
```{r}
a1 <- aov(rc.comp ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$rc.comp, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$rc.comp, list(data3$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$age.tested.c, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$age.tested.c, list(data3$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$wasi.matr.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$wasi.matr.t, list(data3$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$decode, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$decode, list(data3$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = data3)
summary(a1)
pairwise.t.test(data3$ppvt.t, data3$CI_group, p.adjust.method = "bonferroni")
aggregate(data3$ppvt.t, list(data3$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
RC.resi <- data.frame(table(data2$CI_group))
names(RC.resi) <- c("Group","RCi")
```


## Group Sizes
 Across reading comprehension tests
 
```{r, results = "asis"}
group.sizes <- cbind(KTEA.res, KTEA.resi[,2], WJ3.res[,2], WJ3.resi[,2], RC.res[,2], RC.resi[,2])
names(group.sizes) <- c("group", "KTEA No Interaction", "KTEA Interaction", "WJ No Interaction", "WJ Interaction", "Composite No Interaction", "Composite Interaction")
gs <- xtable(group.sizes)
print(gs, type ="html", include.rownames = FALSE)
```

