---
title: "UPC Analysis - Multiple Comprehension Tests"
author: "Kayleigh Ryherd"
date: "8/30/2017"
output: html_document
---

# 15/70 Confidence Intervals 

## Table of Contents

1. [Gates](#gates)
    + [Group Differences](#group-differences-gates)
2. [KTEA](#ktea)
    + [Group Differences](#group-differences-ktea)
3. [ND](#nd)
    + [Group Differences](#group-differences-nd)
4. [WJ](#wj)
    + [Group Differences](#group-differences-wj)
5. [Group Sizes](#group-sizes)

Read in packages & data.
```{r, warning = FALSE, message = FALSE}
library(fBasics)
library(caret)
library(MASS)
library(ggplot2)
library(plyr)
library(reshape2)
library(xtable)
setwd("~/Dropbox/Definition_of_PCs/RegressionDefinitionMethod/MultipleCompTests-Aug2017/RegressionMethod")
dataFiles <- lapply(Sys.glob("All_CDI_*.csv"), read.csv)
cms <- c("GM", "KTEA", "ND", "WJ")
names(dataFiles) <- cms
list2env(dataFiles,envir=.GlobalEnv)
```

Define some functions.

```{r}
# for plotting
gg_color_hue <- function(n) {
  hues = seq(15, 375, length=n+1)
  hcl(h=hues, l=65, c=100)[1:n]
}

# CIs to z-scores
ci2z <- function(ci)
{
  qnorm(ci + (1 - ci)/2)
}
```

```{r}
ci.to.use <- c(.15, .70)
ci.title <- "CIs: 15%, 70%"
ci.doc <- "15_70"
```

## Gates

Run model, get groups.
```{r}
GM2 <- GM[,-c(19:24)]
m1 <- lm(gm.rcomp.cs ~ age.tested.c + decode + wasi.matr.t + ppvt.t, data = GM)

#standardize predicted values
GM2$Pred <- predict(m1)
GM2$stdPred <- scale(GM2$Pred)

#obtained residuals
GM2$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

GM2$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
GM2$CI_group[GM2$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(gm.rcomp.cs ~ stdPred, data=GM2)

p1 <- ggplot(GM2, aes(x=stdPred, y=gm.rcomp.cs)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Gates Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences Gates

```{r}
# take away NSC group
GM3 <- subset(GM2, CI_group != "NSC")
GM3$CI_group <- as.factor(GM3$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(gm.rcomp.cs ~ CI_group, data = GM3)
summary(a1)
pairwise.t.test(GM3$gm.rcomp.cs, GM3$CI_group, p.adjust.method = "bonferroni")
aggregate(GM3$gm.rcomp.cs, list(GM3$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = GM3)
summary(a1)
pairwise.t.test(GM3$age.tested.c, GM3$CI_group, p.adjust.method = "bonferroni")
aggregate(GM3$age.tested.c, list(GM3$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = GM3)
summary(a1)
pairwise.t.test(GM3$wasi.matr.t, GM3$CI_group, p.adjust.method = "bonferroni")
aggregate(GM3$wasi.matr.t, list(GM3$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = GM3)
summary(a1)
pairwise.t.test(GM3$decode, GM3$CI_group, p.adjust.method = "bonferroni")
aggregate(GM3$decode, list(GM3$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = GM3)
summary(a1)
pairwise.t.test(GM3$ppvt.t, GM3$CI_group, p.adjust.method = "bonferroni")
aggregate(GM3$ppvt.t, list(GM3$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
GM.res <- data.frame(table(GM2$CI_group))
names(GM.res) <- c("Group","GM")
```

## KTEA

Run model, get groups.
```{r}
KTEA2 <- KTEA[,-c(19:24)]
m1 <- lm(ktea2.t ~ age.tested.c + decode + wasi.matr.t + ppvt.t, data = KTEA)

#standardize predicted values
KTEA2$Pred <- predict(m1)
KTEA2$stdPred <- scale(KTEA2$Pred)

#obtained residuals
KTEA2$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

KTEA2$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
KTEA2$CI_group[KTEA2$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(ktea2.t ~ stdPred, data=KTEA2)

p1 <- ggplot(KTEA2, aes(x=stdPred, y=ktea2.t)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Gates Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences KTEA

```{r}
# take away NSC group
KTEA3 <- subset(KTEA2, CI_group != "NSC")
KTEA3$CI_group <- as.factor(KTEA3$CI_group)
write.csv(KTEA3, paste("KTEANoInt-",ci.doc,"NoImpute.csv", sep=""))
```

### Reading Comprehension
```{r}
a1 <- aov(ktea2.t ~ CI_group, data = KTEA3)
summary(a1)
pairwise.t.test(KTEA3$ktea2.t, KTEA3$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA3$ktea2.t, list(KTEA3$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = KTEA3)
summary(a1)
pairwise.t.test(KTEA3$age.tested.c, KTEA3$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA3$age.tested.c, list(KTEA3$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = KTEA3)
summary(a1)
pairwise.t.test(KTEA3$wasi.matr.t, KTEA3$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA3$wasi.matr.t, list(KTEA3$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = KTEA3)
summary(a1)
pairwise.t.test(KTEA3$decode, KTEA3$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA3$decode, list(KTEA3$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = KTEA3)
summary(a1)
pairwise.t.test(KTEA3$ppvt.t, KTEA3$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA3$ppvt.t, list(KTEA3$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
KTEA.res <- data.frame(table(KTEA2$CI_group))
names(KTEA.res) <- c("Group","KTEA")
```

## ND

Run model, get groups.
```{r}
ND2 <- ND[,-c(19:24)]
m1 <- lm(nd.rcomp.t ~ age.tested.c + decode + wasi.matr.t + ppvt.t, data = ND)

#standardize predicted values
ND2$Pred <- predict(m1)
ND2$stdPred <- scale(ND2$Pred)

#obtained residuals
ND2$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

ND2$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
ND2$CI_group[ND2$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(nd.rcomp.t ~ stdPred, data=ND2)

p1 <- ggplot(ND2, aes(x=stdPred, y=nd.rcomp.t)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Gates Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences ND

```{r}
# take away NSC group
ND3 <- subset(ND2, CI_group != "NSC")
ND3$CI_group <- as.factor(ND3$CI_group)
```

### Reading Comprehension
```{r}
a1 <- aov(nd.rcomp.t ~ CI_group, data = ND3)
summary(a1)
pairwise.t.test(ND3$nd.rcomp.t, ND3$CI_group, p.adjust.method = "bonferroni")
aggregate(ND3$nd.rcomp.t, list(ND3$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = ND3)
summary(a1)
pairwise.t.test(ND3$age.tested.c, ND3$CI_group, p.adjust.method = "bonferroni")
aggregate(ND3$age.tested.c, list(ND3$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = ND3)
summary(a1)
pairwise.t.test(ND3$wasi.matr.t, ND3$CI_group, p.adjust.method = "bonferroni")
aggregate(ND3$wasi.matr.t, list(ND3$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = ND3)
summary(a1)
pairwise.t.test(ND3$decode, ND3$CI_group, p.adjust.method = "bonferroni")
aggregate(ND3$decode, list(ND3$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = ND3)
summary(a1)
pairwise.t.test(ND3$ppvt.t, ND3$CI_group, p.adjust.method = "bonferroni")
aggregate(ND3$ppvt.t, list(ND3$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
ND.res <- data.frame(table(ND2$CI_group))
names(ND.res) <- c("Group","ND")
```

## WJ

Run model, get groups.
```{r}
WJ2 <- WJ[,-c(19:24)]
m1 <- lm(wj3.rcomp.t ~ age.tested.c + decode + wasi.matr.t + ppvt.t, data = WJ)

#standardize predicted values
WJ2$Pred <- predict(m1)
WJ2$stdPred <- scale(WJ2$Pred)

#obtained residuals
WJ2$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

WJ2$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
WJ2$CI_group[WJ2$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.t ~ stdPred, data=WJ2)

p1 <- ggplot(WJ2, aes(x=stdPred, y=wj3.rcomp.t)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Gates Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences WJ

```{r}
# take away NSC group
WJ3 <- subset(WJ2, CI_group != "NSC")
WJ3$CI_group <- as.factor(WJ3$CI_group)
write.csv(WJ3, paste("WJNoInt-",ci.doc,"NoImpute.csv", sep=""))
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.t ~ CI_group, data = WJ3)
summary(a1)
pairwise.t.test(WJ3$wj3.rcomp.t, WJ3$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3$wj3.rcomp.t, list(WJ3$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = WJ3)
summary(a1)
pairwise.t.test(WJ3$age.tested.c, WJ3$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3$age.tested.c, list(WJ3$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = WJ3)
summary(a1)
pairwise.t.test(WJ3$wasi.matr.t, WJ3$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3$wasi.matr.t, list(WJ3$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = WJ3)
summary(a1)
pairwise.t.test(WJ3$decode, WJ3$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3$decode, list(WJ3$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = WJ3)
summary(a1)
pairwise.t.test(WJ3$ppvt.t, WJ3$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3$ppvt.t, list(WJ3$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
WJ.res <- data.frame(table(WJ2$CI_group))
names(WJ.res) <- c("Group","WJ")
```

## Group Sizes
 Across reading comprehension tests
 
```{r, results = "asis"}
group.sizes <- cbind(GM.res, KTEA.res[,2], ND.res[,2], WJ.res[,2])
names(group.sizes) <- c("group", "GM", "KTEA", "ND", "WJ")
gs <- xtable(group.sizes)
print(gs, type ="html", include.rownames = FALSE)
```
