---
title: "UPC Analysis - KTEA & GM, imputed data"
author: "Kayleigh Ryherd"
date: "9/13/2017"
output: html_document
---

# 15/60 Confidence Intervals 

## Table of Contents

1. [KTEA](#ktea)
2. [WJ](#wj)
3. [Group Sizes](#group-sizes)

Read in packages & data.
```{r, warning = FALSE, message = FALSE}
library(fBasics)
library(caret)
library(MASS)
library(ggplot2)
library(plyr)
library(reshape2)
library(xtable)
setwd("~/Dropbox/Definition_of_PCs/RegressionDefinitionMethod/MultipleCompTests-Aug2017/RegressionMethod")
data <- read.csv("classification.csv")
rc.comp <- read.csv("comprehension_composite.csv")
rc.composite <- rc.comp[,-1]
data2 <- merge(data, rc.composite, by = "SubjectID")
WJ3 <- data2
KTEA <- data2
```

Define some functions.

```{r}
# for plotting
gg_color_hue <- function(n) {
  hues = seq(15, 375, length=n+1)
  hcl(h=hues, l=65, c=100)[1:n]
}

# CIs to z-scores
ci2z <- function(ci)
{
  qnorm(ci + (1 - ci)/2)
}
```

```{r}
ci.to.use <- c(.15, .60)
ci.title <- "CIs: 15%, 60%"
ci.doc <- "15_60"
```

## KTEA

# No interaction

Run model, get groups.
```{r}

m1 <- lm(ktea2.t ~ age.tested.c + decode + wasi.matr.t + ppvt.t, data = KTEA)

#standardize predicted values
KTEA$Pred <- predict(m1)
KTEA$stdPred <- scale(KTEA$Pred)

#obtained residuals
KTEA$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

KTEA$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
KTEA$CI_group[KTEA$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(ktea2.t ~ stdPred, data=KTEA)

p1 <- ggplot(KTEA, aes(x=stdPred, y=ktea2.t)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Gates Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences KTEA

```{r}
# take away NSC group
KTEA2 <- subset(KTEA, CI_group != "NSC")
KTEA2$CI_group <- as.factor(KTEA2$CI_group)
write.csv(KTEA2, paste("KTEANoInt-",ci.doc,".csv", sep=""))
```

### Reading Comprehension
```{r}
a1 <- aov(ktea2.t ~ CI_group, data = KTEA2)
summary(a1)
pairwise.t.test(KTEA2$ktea2.t, KTEA2$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA2$ktea2.t, list(KTEA2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = KTEA2)
summary(a1)
pairwise.t.test(KTEA2$age.tested.c, KTEA2$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA2$age.tested.c, list(KTEA2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = KTEA2)
summary(a1)
pairwise.t.test(KTEA2$wasi.matr.t, KTEA2$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA2$wasi.matr.t, list(KTEA2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = KTEA2)
summary(a1)
pairwise.t.test(KTEA2$decode, KTEA2$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA2$decode, list(KTEA2$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = KTEA2)
summary(a1)
pairwise.t.test(KTEA2$ppvt.t, KTEA2$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA2$ppvt.t, list(KTEA2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
KTEA.res <- data.frame(table(KTEA$CI_group))
names(KTEA.res) <- c("Group","KTEA")
```

# Interaction

Run model, get groups.
```{r}

m1 <- lm(ktea2.t ~ age.tested.c * decode * wasi.matr.t * ppvt.t, data = KTEA)

KTEAi <- KTEA

#standardize predicted values
KTEAi$Pred <- predict(m1)
KTEAi$stdPred <- scale(KTEAi$Pred)

#obtained residuals
KTEAi$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

KTEAi$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
KTEAi$CI_group[KTEAi$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(ktea2.t ~ stdPred, data=KTEAi)

p1 <- ggplot(KTEAi, aes(x=stdPred, y=ktea2.t)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Gates Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences KTEA

```{r}
# take away NSC group
KTEA2 <- subset(KTEAi, CI_group != "NSC")
KTEA2$CI_group <- as.factor(KTEA2$CI_group)
write.csv(KTEA2, paste("KTEAInt-",ci.doc,".csv", sep=""))
```

### Reading Comprehension
```{r}
a1 <- aov(ktea2.t ~ CI_group, data = KTEA2)
summary(a1)
pairwise.t.test(KTEA2$ktea2.t, KTEA2$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA2$ktea2.t, list(KTEA2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = KTEA2)
summary(a1)
pairwise.t.test(KTEA2$age.tested.c, KTEA2$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA2$age.tested.c, list(KTEA2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = KTEA2)
summary(a1)
pairwise.t.test(KTEA2$wasi.matr.t, KTEA2$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA2$wasi.matr.t, list(KTEA2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = KTEA2)
summary(a1)
pairwise.t.test(KTEA2$decode, KTEA2$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA2$decode, list(KTEA2$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = KTEA2)
summary(a1)
pairwise.t.test(KTEA2$ppvt.t, KTEA2$CI_group, p.adjust.method = "bonferroni")
aggregate(KTEA2$ppvt.t, list(KTEA2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
KTEA.resi <- data.frame(table(KTEA$CI_group))
names(KTEA.resi) <- c("Group","KTEA")
```

## WJ

# No interaction

Run model, get groups.
```{r}

m1 <- lm(wj3.rcomp.t ~ age.tested.c + decode + wasi.matr.t + ppvt.t, data = WJ3)

#standardize predicted values
WJ3$Pred <- predict(m1)
WJ3$stdPred <- scale(WJ3$Pred)

#obtained residuals
WJ3$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

WJ3$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
WJ3$CI_group[WJ3$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.t ~ stdPred, data=WJ3)

p1 <- ggplot(WJ3, aes(x=stdPred, y=wj3.rcomp.t)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Gates Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences WJ

```{r}
# take away NSC group
WJ3_2 <- subset(WJ3, CI_group != "NSC")
WJ3_2$CI_group <- as.factor(WJ3_2$CI_group)
write.csv(WJ3_2, paste("WJNoInt-",ci.doc,".csv", sep=""))
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.t ~ CI_group, data = WJ3_2)
summary(a1)
pairwise.t.test(WJ3_2$wj3.rcomp.t, WJ3_2$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3_2$wj3.rcomp.t, list(WJ3_2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = WJ3_2)
summary(a1)
pairwise.t.test(WJ3_2$age.tested.c, WJ3_2$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3_2$age.tested.c, list(WJ3_2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = WJ3_2)
summary(a1)
pairwise.t.test(WJ3_2$wasi.matr.t, WJ3_2$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3_2$wasi.matr.t, list(WJ3_2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = WJ3_2)
summary(a1)
pairwise.t.test(WJ3_2$decode, WJ3_2$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3_2$decode, list(WJ3_2$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = WJ3_2)
summary(a1)
pairwise.t.test(WJ3_2$ppvt.t, WJ3_2$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3_2$ppvt.t, list(WJ3_2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
WJ3.res <- data.frame(table(WJ3$CI_group))
names(WJ3.res) <- c("Group","WJ")
```

# Interaction
Run model, get groups.
```{r}

m1 <- lm(wj3.rcomp.t ~ age.tested.c * decode * wasi.matr.t * ppvt.t, data = WJ3)

WJ3i <- WJ3

#standardize predicted values
WJ3i$Pred <- predict(m1)
WJ3i$stdPred <- scale(WJ3i$Pred)

#obtained residuals
WJ3i$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

WJ3i$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
WJ3i$CI_group[WJ3i$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(wj3.rcomp.t ~ stdPred, data=WJ3i)

p1 <- ggplot(WJ3i, aes(x=stdPred, y=wj3.rcomp.t)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Gates Reading Comprehension") +
  ggtitle(ci.title)
```

## Group Differences WJ

```{r}
# take away NSC group
WJ3_2 <- subset(WJ3i, CI_group != "NSC")
WJ3_2$CI_group <- as.factor(WJ3_2$CI_group)
write.csv(WJ3_2, paste("WJInt-",ci.doc,".csv", sep=""))
```

### Reading Comprehension
```{r}
a1 <- aov(wj3.rcomp.t ~ CI_group, data = WJ3_2)
summary(a1)
pairwise.t.test(WJ3_2$wj3.rcomp.t, WJ3_2$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3_2$wj3.rcomp.t, list(WJ3_2$CI_group), mean)
```

### Age
```{r}
a1 <- aov(age.tested.c ~ CI_group, data = WJ3_2)
summary(a1)
pairwise.t.test(WJ3_2$age.tested.c, WJ3_2$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3_2$age.tested.c, list(WJ3_2$CI_group), mean)
```

### Matrix Reasoning
```{r}
a1 <- aov(wasi.matr.t ~ CI_group, data = WJ3_2)
summary(a1)
pairwise.t.test(WJ3_2$wasi.matr.t, WJ3_2$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3_2$wasi.matr.t, list(WJ3_2$CI_group), mean)
```

### Decoding
```{r}
a1 <- aov(decode~ CI_group, data = WJ3_2)
summary(a1)
pairwise.t.test(WJ3_2$decode, WJ3_2$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3_2$decode, list(WJ3_2$CI_group), mean)
```

### PPVT 
```{r}
a1 <- aov(ppvt.t ~ CI_group, data = WJ3_2)
summary(a1)
pairwise.t.test(WJ3_2$ppvt.t, WJ3_2$CI_group, p.adjust.method = "bonferroni")
aggregate(WJ3_2$ppvt.t, list(WJ3_2$CI_group), mean)
```

Show group sizes, plot.
```{r}
print(p1)
WJ3.resi <- data.frame(table(WJ3$CI_group))
names(WJ3.resi) <- c("Group","WJ")
```

## RC Composite

```{r}

m1 <- lm(rc.comp ~ age.tested.c + decode + wasi.matr.t + ppvt.t, data = data2)

#standardize predicted values
data2$Pred <- predict(m1)
data2$stdPred <- scale(data2$Pred)

#obtained residuals
data2$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

data2$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
data2$CI_group[data2$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(ktea2.t ~ stdPred, data=data2)

p1 <- ggplot(data2, aes(x=stdPred, y=rc.comp)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Gates Reading Comprehension") +
  ggtitle(ci.title)
```

```{r}
# take away NSC group
data3 <- subset(data2, CI_group != "NSC")
data3$CI_group <- as.factor(data3$CI_group)
write.csv(data3, paste("CompositeNoInt-",ci.doc,".csv", sep=""))
```

```{r}
data2i <- data2

m1 <- lm(rc.comp ~ age.tested.c * decode * wasi.matr.t * ppvt.t, data = data2i)

#standardize predicted values
data2i$Pred <- predict(m1)
data2i$stdPred <- scale(data2i$Pred)

#obtained residuals
data2i$resid <- resid <- residuals(m1)
qqnorm(scale(resid)); qqline(scale(resid))

#create the range of SD (z value) bins 
my.bin <- c(range(scale(resid))+.1, ci2z(ci.to.use), -ci2z(ci.to.use))
#we could also manually specify in terms of SDs
# my.bin <- c(-3, -1, -.25, .25, 1, 3)
my.bin <- sort(my.bin)
# names for each bin specified above
grouping <- c("UPC", "NSC", "EAC", "NSC", "UGC")

data2i$CI_group <- grouping[findInterval(scale(resid), vec=my.bin, all.inside=T)]
#those with Standardized Predicted Value below -1 should be "EPC"
data2i$CI_group[data2i$stdPred < -1] <- "EPC"

### there are five groups c("EAC", "NSC", "UGC", "UPC", "EPC")
### so the argument n = 5
my.col <- gg_color_hue(n=5)

## unscale the z value for each CI, so I can add that value to intercept
unscale.ci <- my.bin[-c(1,length(my.bin))]*sd(resid)+mean(resid)

## create plot
m2 <- lm(ktea2.t ~ stdPred, data=data2i)

p1 <- ggplot(data2i, aes(x=stdPred, y=rc.comp)) + geom_point(aes(color=CI_group)) + 
  geom_abline(intercept = coef(m2)[1], slope = coef(m2)[2]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[2], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[3], slope = coef(m2)[2], color=my.col[1]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[1], slope = coef(m2)[2], color=my.col[4]) +
  geom_abline(intercept = coef(m2)[1] + unscale.ci[4], slope = coef(m2)[2], color=my.col[3]) +
  geom_vline(xintercept = -1, lty="dotted") + 
  xlab("Standardized Predicted Value")+ylab("Gates Reading Comprehension") +
  ggtitle(ci.title)
```

```{r}
# take away NSC group
data3i <- subset(data2i, CI_group != "NSC")
data3i$CI_group <- as.factor(data3i$CI_group)
write.csv(data3i, paste("CompositeInt-",ci.doc,".csv", sep=""))
```


## Group Sizes
 Across reading comprehension tests
 
```{r, results = "asis"}
group.sizes <- cbind(KTEA.res, KTEA.resi[,2], WJ3.res[,2], WJ3.resi[,2])
names(group.sizes) <- c("group", "KTEA No Interaction", "KTEA Interaction", "WJ No Interaction", "WJ Interaction")
gs <- xtable(group.sizes)
print(gs, type ="html", include.rownames = FALSE)
```

