---
title: "Checking for Influential Points"
author: "Kayleigh Ryherd"
date: "11/17/2017"
output: html_document
---


Read in packages & data.
```{r, warning = FALSE, message = FALSE}
library(fBasics)
library(caret)
library(MASS)
library(ggplot2)
library(plyr)
library(reshape2)
library(xtable)
setwd("~/Dropbox/Definition_of_PCs/RegressionDefinitionMethod/MultipleCompTests-Aug2017/RegressionMethod/influentialpoints")
data <- read.csv("classification.csv")
KTEA <- data
```

```{r}

m1 <- lm(ktea2.t ~ age.tested.c + decode + wasi.matr.t + ppvt.t, data = KTEA)
cooksd <- cooks.distance(m1)

plot(cooksd, pch="*", cex=2, main="Influential Obs by Cooks distance")  # plot cook's distance
abline(h = 4*mean(cooksd, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksd)+1, y=cooksd, labels=ifelse(cooksd>4*mean(cooksd, na.rm=T),names(cooksd),""), col="red")  # add labels

influential <- as.numeric(names(cooksd)[(cooksd > 4*mean(cooksd, na.rm=T))])  # influential row numbers
inf.p <- KTEA[influential, ]
inf.p <- inf.p[,c(1,3,13,15,17,21)]
head(inf.p)
```
44 total influential subjects.

Checking to see how may of the 44 subjects were used in the MRI analysis.

```{r}
data2 <- read.csv("KTEANoInt15_65-imputed.csv")
merge <- merge(data2, inf.p, by = "SubjectID")
print(merge, digits = 2)
```

19 of the influential subjects were used in the MRI analysis.

Most of the subjects are only influential due to age (their other scores have a z-score between -2 and 2).

Here are the remaining subjects (there are only 4):

```{r}
rel <- c(1204,1000,62,220)
inf.p2 <- inf.p[is.element(inf.p$SubjectID, rel), ]
inf.p2
```

Here are the ones used for the MRI analysis:
 
62 (UPC)  
1000 (UPC)



